Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-06 WSSSPE1_report/WSSSPE1_summary_report.tex
fixing order of attendees in a way that should be easy to add new people later

\usepackage{color}
\usepackage{dcolumn}
\usepackage{float}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage{psfrag}
\usepackage{tabularx}
\usepackage[hyphens]{url}
\usepackage{wrapfig}
\usepackage{enumitem}

@@

\note{should alphabetize all, but if we get more from the SC13 folks, it's not worth spending
time doing this now.  I wonder if there's a way to just have a simple list that we can keep ordered, and let LaTeX do the formatting, rather than manually creating a table as this is now}

The following is a partial list of attendees who were recorded on the
Google doc that was being used for live note taking at the workshop:

\begin{tabular}{ L{4cm}  L{4cm}  L{4cm}  L{4cm} }
   Daniel S. Katz
&  Neil Chue Hong
&  Gabrielle Allen
&  David Proctor
\\ Manish Parashar
&  Jay Alameda
&  David Andrs
&  Lorena A Barba
\\ David Bernholdt
&  Phil Bourne
&  Karl Broman
&  Maxine Brown
\\ David Bruhwiler
&  Bruno Bzeznik
&  Jeffrey Carver
&  John W. Cobb
\\ Karen Cranston
&  Rion Dooley
&  Anshu Dubey
&  Ian Foster
\\Juliana Freire
& Derek Gaston
& Derek Groen
& Edmund Hart
\\James Hetherington
& Simon Hettrick
& Kenneth Hoste
& James Howison
\\Daisie Huang
& Kerk Kee
& Arnaud Legrand
& Paul Madden
\\Louis Maddox
& Ketan Maheshwari
& Suresh Marru
& Cezary Mazurek
\\James McClure
& Chris Mentzel
& J. Yates Monteith
& Pierre Neyron
\\Lucas Nussbaum
& Cody Permann
& John Peterson
& Quan Pham
\\Marlon Pierce
& Heather Piwowar
& Jason Riedy
& Andreas Schreiber
\\William Scullin
& Andrew Slaughter
& Arfon Smith
& James Spencer
\\Shel Swenson
& Fr\'{e}d\'{e}ric Suter
& Andy Terrel
& George  Thiruvathukal
\\John Towns
& Erik Trainer
& Matthew Turk
& Eric Van Wyk
\\Colin C. Venters
& Von Welch
& Nancy Wilkins-Diehr
& Theresa Windus
\\Rich Wolski
& Lynn Zentner
& Frank L\"{o}ffler
& Patrick O'Leary
\end{tabular}

>>>>

\usepackage{color}
\usepackage{dcolumn}
\usepackage{float}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage{psfrag}
\usepackage{tabularx}
\usepackage[hyphens]{url}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{multicol}

@@

The following is a partial list of attendees who were recorded on the
Google doc~\cite{WSSSPE1-google-notes} that was being used for live note taking at the workshop, with some additions made by the authors of this paper.

\begin{multicols}{4}
\setlength{\parindent}{0pt}
%in theory, should save the old value then set it back after this section, but since this is the end...

Jay Alameda

Gabrielle Allen

David Andrs

Lorena A Barba

David Bernholdt

Phil Bourne

Karl Broman

Maxine Brown

David Bruhwiler

Bruno Bzeznik

Jeffrey Carver

Neil Chue Hong

John W. Cobb

Karen Cranston

Rion Dooley

Anshu Dubey

Ian Foster

Juliana Freire

Derek Gaston

Derek Groen

Edmund Hart

James Hetherington

Simon Hettrick

Kenneth Hoste

James Howison

Daisie Huang

Daniel S. Katz

Kerk Kee

Arnaud Legrand

Frank L\"{o}ffler

Paul Madden

Louis Maddox

Ketan Maheshwari

Suresh Marru

Cezary Mazurek

James McClure

Chris Mentzel

J. Yates Monteith

Pierre Neyron

Lucas Nussbaum

Patrick O'Leary

Manish Parashar

Cody Permann

John Peterson

Quan Pham

Marlon Pierce

Heather Piwowar

David Proctor

Jason Riedy

Andreas Schreiber

William Scullin

Andrew Slaughter

Arfon Smith

James Spencer

Shel Swenson

Fr\'{e}d\'{e}ric Suter

Andy Terrel

George  Thiruvathukal

John Towns

Erik Trainer

Matthew Turk

Eric Van Wyk

Colin C. Venters

Von Welch

Nancy Wilkins-Diehr

Theresa Windus

Rich Wolski

Lynn Zentner

\end{multicols}
